---
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_caption: true
    keep_tex: false
    latex_engine: xelatex
    extra_dependencies: ["booktabs", "float", "amsmath", "geometry"]
    includes:
      in_header: headerAE.tex
      before_body: titlepageAE.tex
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: flatly
    highlight: tango
    number_sections: true
    code_folding: show
geometry: "margin=2.5cm"
fontsize: 12pt
linestretch: 1.5
header-includes:
  - \usepackage{booktabs}
  - \usepackage{float}
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \usepackage{fancyhdr}
  - \usepackage{titling}
  - \usepackage{abstract}

---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  warning   = FALSE,
  message   = FALSE,
  fig.align = "center",
  fig.width  = 6,
  fig.height = 3.5,
  out.width  = "90%"
)
```


---

# Data

## Loading and Preparing the Data

```{r libraries, message=FALSE, warning=FALSE}
# Uncomment to install if needed:
# install.packages(c("tidyverse","plm","lmtest","stargazer",
#                    "ggplot2","car","forecast","tseries","kableExtra","scales"))

library(tidyverse)
library(plm)
library(lmtest)
library(stargazer)
library(ggplot2)
library(car)
library(forecast)
library(tseries)
library(zoo)
library(kableExtra)
library(scales)
```

```{r load-data}
# Load the dataset — make sure the CSV is in your working directory
data_raw <- read.csv("panel_data_8countries.csv", stringsAsFactors = FALSE)

cat("Dimensions:", nrow(data_raw), "rows x", ncol(data_raw), "columns\n")
glimpse(data_raw)
```

```{r process-data}
# Define country groups
emerging_importers <- c("Turkey", "Poland", "India",
                        "Indonesia", "South_Africa", "Thailand")
advanced_exporters <- c("United_States", "Canada")

# Process data: parse dates, compute log variables, post-crisis dummy
data_processed <- data_raw %>%
  mutate(
    date        = as.Date(date, format = "%d/%m/%Y"),
    ln_cpi      = log(cpi),
    ln_ipi      = log(ipi),
    ln_neer     = log(neer),
    post_crisis = as.integer(date >= as.Date("2026-03-01")),
    oil_balance = if_else(country %in% advanced_exporters,
                          "Exporter", "Importer"),
    dev_level   = if_else(country %in% advanced_exporters,
                          "Advanced", "Emerging"),
    group       = paste(dev_level, oil_balance, sep = "_")
  )

# Compute oil shock from Brent series (recalculated, not taken from CSV)
oil_shock_lookup <- data_processed %>%
  distinct(date, brent) %>%
  arrange(date) %>%
  mutate(oil_pct_change = c(0, diff(brent) / head(brent, -1) * 100))

data_processed <- data_processed %>%
  { if ("oil_pct_change" %in% names(.)) select(., -oil_pct_change) else . } %>%
  left_join(oil_shock_lookup %>% select(date, oil_pct_change), by = "date")

cat("\nDate range:", as.character(min(data_processed$date)),
    "to", as.character(max(data_processed$date)))
cat("\nCountries:", paste(sort(unique(data_processed$country)), collapse = ", "))
cat("\nTotal observations:", nrow(data_processed), "\n")
```

## Descriptive Statistics

```{r summary-table}
data_processed %>%
  select(ln_cpi, ln_ipi, oil_pct_change,
         ln_neer, policy_rate, vix, brent) %>%
  summarise(across(everything(),
    list(Mean = ~round(mean(.), 3), SD   = ~round(sd(.), 3),
         Min  = ~round(min(.), 3),  Max  = ~round(max(.), 3)),
    .names = "{.col}__{.fn}")) %>%
  pivot_longer(everything(),
               names_to  = c("Variable", "Stat"),
               names_sep = "__") %>%
  pivot_wider(names_from = Stat, values_from = value) %>%
  mutate(Variable = case_match(Variable,
    "ln_cpi"         ~ "ln(CPI)",
    "ln_ipi"         ~ "ln(IPI)",
    "oil_pct_change" ~ "Oil Shock (%)",
    "ln_neer"        ~ "ln(NEER)",
    "policy_rate"    ~ "Policy Rate (%)",
    "vix"            ~ "VIX",
    "brent"          ~ "Brent (USD/bbl)",
    .default         = Variable
  )) %>%
  kbl(caption = "Descriptive Statistics — Full Panel (Jan 2023 – Jun 2026)",
      digits = 3, align = "lrrrr", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  footnote(general = "N = 336 observations. 8 countries × 42 months.",
           general_title = "Note:")
```

---

# Exploratory Data Analysis

## Brent Crude Oil Price

```{r plot-oil, fig.cap="Brent Crude Oil Price: Pre- and Post-2026 Gulf Crisis"}
oil_ts <- data_processed %>% distinct(date, brent) %>% arrange(date)

ggplot(oil_ts, aes(x = date, y = brent)) +
  geom_area(fill = "#c0392b", alpha = 0.12) +
  geom_line(color = "#c0392b", linewidth = 1.1) +
  geom_vline(xintercept = as.numeric(as.Date("2026-02-27")),
             linetype = "dashed", color = "#2c3e50", linewidth = 0.9) +
  annotate("label", x = as.numeric(as.Date("2026-02-27")),
           y = max(oil_ts$brent) * 0.88,
           label = "Gulf Crisis\nFeb 27, 2026",
           color = "#2c3e50", size = 3.5, hjust = 1.08,
           fill = "white", label.size = 0.3) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  labs(title    = "Brent Crude Oil Price: Pre- and Post-2026 Gulf Crisis",
       subtitle = "Monthly average, USD per barrel",
       x = NULL, y = "USD / Barrel") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank())
```

## Monthly Oil Shock Variable

```{r plot-shock, fig.cap="Monthly Percentage Change in Brent Crude (OilShock variable)"}
oil_chg <- oil_shock_lookup %>%
  mutate(direction = ifelse(oil_pct_change >= 0, "Increase", "Decrease"))

ggplot(oil_chg, aes(x = date, y = oil_pct_change, fill = direction)) +
  geom_col() +
  geom_hline(yintercept = 0, linewidth = 0.5) +
  geom_vline(xintercept = as.numeric(as.Date("2026-02-27")),
             linetype = "dashed", color = "#2c3e50") +
  scale_fill_manual(values = c("Increase" = "#27ae60",
                               "Decrease" = "#e74c3c"), name = NULL) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  labs(title    = "Monthly % Change in Brent Crude Oil Price",
       subtitle = "The OilShock variable used in regression; dashed line = Gulf Crisis",
       x = NULL, y = "% Change") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        legend.position = "none")
```

## CPI Trends by Country Group

```{r plot-cpi, fig.cap="Log CPI Trends: Emerging Importers vs Advanced Exporters"}
avg_cpi <- data_processed %>%
  group_by(date, group) %>%
  summarise(mean_ln_cpi = mean(ln_cpi), .groups = "drop")

ggplot(avg_cpi, aes(x = date, y = mean_ln_cpi, color = group)) +
  geom_line(linewidth = 1.2) +
  geom_vline(xintercept = as.numeric(as.Date("2026-02-27")),
             linetype = "dashed", color = "black") +
  scale_color_manual(values = c("Emerging_Importer" = "#e74c3c",
                                "Advanced_Exporter"  = "#2980b9"),
                     labels = c("Emerging_Importer" = "Emerging Importers",
                                "Advanced_Exporter"  = "Advanced Exporters")) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  labs(title    = "Log CPI Trends by Country Group",
       subtitle = "Group averages; dashed line = Gulf Crisis start (Feb 27, 2026)",
       x = NULL, y = "Log(CPI)", color = NULL) +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        legend.position = "bottom")
```

## IPI Trends by Country Group

```{r plot-ipi, fig.cap="Log IPI Trends: Emerging Importers vs Advanced Exporters"}
avg_ipi <- data_processed %>%
  group_by(date, group) %>%
  summarise(mean_ln_ipi = mean(ln_ipi), .groups = "drop")

ggplot(avg_ipi, aes(x = date, y = mean_ln_ipi, color = group)) +
  geom_line(linewidth = 1.2) +
  geom_vline(xintercept = as.numeric(as.Date("2026-02-27")),
             linetype = "dashed", color = "black") +
  scale_color_manual(values = c("Emerging_Importer" = "#e74c3c",
                                "Advanced_Exporter"  = "#2980b9"),
                     labels = c("Emerging_Importer" = "Emerging Importers",
                                "Advanced_Exporter"  = "Advanced Exporters")) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b %Y") +
  labs(title    = "Log IPI Trends by Country Group",
       subtitle = "Group averages; dashed line = Gulf Crisis start (Feb 27, 2026)",
       x = NULL, y = "Log(IPI)", color = NULL) +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        legend.position = "bottom")
```

---

# ARIMA Forecasting — June 2026

## Stationarity Tests

```{r adf-tests}
brent_ts <- oil_ts %>% pull(brent) %>% ts(frequency = 12)

cat("=== ADF Test: Brent Oil Price (levels) ===\n")
print(adf.test(brent_ts))

cat("\n=== ADF Test: Brent Oil Price (1st difference) ===\n")
print(adf.test(diff(brent_ts)))
```

## Brent Crude Forecast — June 2026

```{r arima-brent, fig.cap="ARIMA Forecast: Brent Crude Oil Price for June 2026"}
arima_brent <- auto.arima(brent_ts, seasonal = TRUE,
                           stepwise = FALSE, approximation = FALSE,
                           trace = FALSE)
cat("Best ARIMA model for Brent:\n"); print(arima_brent)

fc_brent <- forecast(arima_brent, h = 1)
autoplot(fc_brent) +
  labs(title    = "ARIMA Forecast: Brent Crude Oil — June 2026",
       subtitle = paste0("Model: ARIMA(",
                         paste(arima_brent$arma[c(1,6,2)], collapse = ","), ")"),
       x = "Time (months since Jan 2023)", y = "USD / Barrel") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"))

cat(sprintf("\n-- June 2026 Brent Forecast --\n"))
cat(sprintf("  Point forecast : $%.2f / barrel\n",  fc_brent$mean[1]))
cat(sprintf("  80%% PI        : [$%.2f, $%.2f]\n",
            fc_brent$lower[1,1], fc_brent$upper[1,1]))
cat(sprintf("  95%% PI        : [$%.2f, $%.2f]\n",
            fc_brent$lower[1,2], fc_brent$upper[1,2]))
```

## CPI Forecasts — All 8 Countries

```{r arima-cpi-loop}
countries_list <- sort(unique(data_processed$country))

cpi_forecasts <- tibble(Country = character(), Model = character(),
                        Forecast_CPI = numeric(), PI_80_Low = numeric(),
                        PI_80_High = numeric(), PI_95_Low = numeric(),
                        PI_95_High = numeric())

for (ctry in countries_list) {
  cpi_ts <- data_processed %>%
    filter(country == ctry) %>% arrange(date) %>%
    pull(ln_cpi) %>%
    ts(frequency = 12, start = c(2023, 1))

  fit <- auto.arima(cpi_ts, seasonal = TRUE,
                    stepwise = FALSE, approximation = FALSE, trace = FALSE)
  fc  <- forecast(fit, h = 1)

  cpi_forecasts <- bind_rows(cpi_forecasts, tibble(
    Country      = ctry,
    Model        = paste0("ARIMA(", paste(fit$arma[c(1,6,2)], collapse = ","), ")"),
    Forecast_CPI = round(exp(fc$mean[1]),    4),
    PI_80_Low    = round(exp(fc$lower[1,1]), 4),
    PI_80_High   = round(exp(fc$upper[1,1]), 4),
    PI_95_Low    = round(exp(fc$lower[1,2]), 4),
    PI_95_High   = round(exp(fc$upper[1,2]), 4)
  ))
}

cpi_forecasts %>%
  kbl(caption = "ARIMA Forecasted CPI Level — June 2026",
      col.names = c("Country", "Model", "CPI Forecast",
                    "80% Low", "80% High", "95% Low", "95% High"),
      align = "lcrrrrr", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  column_spec(3, bold = TRUE, color = "#c0392b")
```

## IPI Forecasts — All 8 Countries

```{r arima-ipi-loop}
ipi_forecasts <- tibble(Country = character(), Model = character(),
                        Forecast_IPI = numeric(), PI_80_Low = numeric(),
                        PI_80_High = numeric(), PI_95_Low = numeric(),
                        PI_95_High = numeric())

for (ctry in countries_list) {
  ipi_ts <- data_processed %>%
    filter(country == ctry) %>% arrange(date) %>%
    pull(ln_ipi) %>%
    ts(frequency = 12, start = c(2023, 1))

  fit <- auto.arima(ipi_ts, seasonal = TRUE,
                    stepwise = FALSE, approximation = FALSE, trace = FALSE)
  fc  <- forecast(fit, h = 1)

  ipi_forecasts <- bind_rows(ipi_forecasts, tibble(
    Country      = ctry,
    Model        = paste0("ARIMA(", paste(fit$arma[c(1,6,2)], collapse = ","), ")"),
    Forecast_IPI = round(exp(fc$mean[1]),    4),
    PI_80_Low    = round(exp(fc$lower[1,1]), 4),
    PI_80_High   = round(exp(fc$upper[1,1]), 4),
    PI_95_Low    = round(exp(fc$lower[1,2]), 4),
    PI_95_High   = round(exp(fc$upper[1,2]), 4)
  ))
}

ipi_forecasts %>%
  kbl(caption = "ARIMA Forecasted IPI Level — June 2026",
      col.names = c("Country", "Model", "IPI Forecast",
                    "80% Low", "80% High", "95% Low", "95% High"),
      align = "lcrrrrr", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  column_spec(3, bold = TRUE, color = "#27ae60")
```

---

# Panel Regression — Main Group: Emerging Importers

## Declare Panel Frame

```{r panel-emerging}
pdata_emg <- data_processed %>%
  filter(country %in% emerging_importers) %>%
  pdata.frame(index = c("country", "date"))

cat("Panel: Emerging Importers\n")
cat("Countries :", pdim(pdata_emg)$nT$n, "\n")
cat("Periods   :", pdim(pdata_emg)$nT$T, "\n")
cat("Balanced  :", pdim(pdata_emg)$balanced, "\n")
cat("Observations:", pdim(pdata_emg)$nT$n * pdim(pdata_emg)$nT$T, "\n")
```

## CPI Models — Emerging Importers

```{r cpi-emg-models}
formula_cpi <- ln_cpi ~ oil_pct_change + ln_neer +
                        policy_rate + vix + post_crisis

pols_cpi_emg <- plm(formula_cpi, data = pdata_emg, model = "pooling")
fe_cpi_emg   <- plm(formula_cpi, data = pdata_emg, model = "within")
re_cpi_emg   <- plm(formula_cpi, data = pdata_emg, model = "random")
```

```{r cpi-emg-table, results='asis'}

stargazer(pols_cpi_emg, fe_cpi_emg, re_cpi_emg,
          title          = "CPI Regression — Emerging Importers",
          column.labels  = c("Pooled OLS", "Fixed Effects", "Random Effects"),
          dep.var.labels = "ln(CPI)",
          covariate.labels = c("Oil Shock (% $\\Delta$ Brent)",
                               "ln(NEER)", "Policy Rate (%)",
                               "VIX", "Post-Crisis Dummy"),
          keep.stat      = c("n", "rsq", "adj.rsq"),
          type           = "latex", style = "aer",
          digits         = 6,
          digits.extra   = 4,
          notes          = "Arellano HC3 robust SE applied in Section 8.",
          notes.align    = "l")
```

## IPI Models — Emerging Importers

```{r ipi-emg-models}
formula_ipi <- ln_ipi ~ oil_pct_change + ln_neer +
                        policy_rate + vix + post_crisis

pols_ipi_emg <- plm(formula_ipi, data = pdata_emg, model = "pooling")
fe_ipi_emg   <- plm(formula_ipi, data = pdata_emg, model = "within")
re_ipi_emg   <- plm(formula_ipi, data = pdata_emg, model = "random")
```

```{r ipi-emg-table, results='asis'}

stargazer(pols_ipi_emg, fe_ipi_emg, re_ipi_emg,
          title          = "IPI Regression — Emerging Importers",
          column.labels  = c("Pooled OLS", "Fixed Effects", "Random Effects"),
          dep.var.labels = "ln(IPI)",
          covariate.labels = c("Oil Shock (% $\\Delta$ Brent)",
                               "ln(NEER)", "Policy Rate (%)",
                               "VIX", "Post-Crisis Dummy"),
          keep.stat      = c("n", "rsq", "adj.rsq"),
          type           = "latex", style = "aer",
          digits         = 6,
          digits.extra   = 4,
          notes          = "Arellano HC3 robust SE applied in Section 8.",
          notes.align    = "l")
```

---

# Panel Regression — Comparison Group: Advanced Exporters

## Declare Panel Frame

```{r panel-advanced}
pdata_adv <- data_processed %>%
  filter(country %in% advanced_exporters) %>%
  pdata.frame(index = c("country", "date"))

cat("Panel: Advanced Exporters\n")
cat("Countries :", pdim(pdata_adv)$nT$n, "\n")
cat("Periods   :", pdim(pdata_adv)$nT$T, "\n")
cat("Balanced  :", pdim(pdata_adv)$balanced, "\n")
cat("Observations:", pdim(pdata_adv)$nT$n * pdim(pdata_adv)$nT$T, "\n")
```

## CPI Models — Advanced Exporters

```{r cpi-adv-models}
pols_cpi_adv <- plm(formula_cpi, data = pdata_adv, model = "pooling")
fe_cpi_adv   <- plm(formula_cpi, data = pdata_adv, model = "within")
re_cpi_adv <- plm(formula_cpi, data = pdata_adv, model = "random",
                  random.method = "walhus")  # or "amemiya"
```

```{r cpi-adv-table, results='asis'}

stargazer(pols_cpi_adv, fe_cpi_adv, re_cpi_adv,
          title          = "CPI Regression — Advanced Exporters",
          column.labels  = c("Pooled OLS", "Fixed Effects", "Random Effects"),
          dep.var.labels = "ln(CPI)",
          covariate.labels = c("Oil Shock (% $\\Delta$ Brent)",
                               "ln(NEER)", "Policy Rate (%)",
                               "VIX", "Post-Crisis Dummy"),
          keep.stat      = c("n", "rsq", "adj.rsq"),
          type           = "latex", style = "aer",
          digits         = 6,
          digits.extra   = 4,
          notes          = "Arellano HC3 robust SE applied in Section 8.",
          notes.align    = "l")
```

## IPI Models — Advanced Exporters

```{r ipi-adv-models}
pols_ipi_adv <- plm(formula_ipi, data = pdata_adv, model = "pooling")
fe_ipi_adv   <- plm(formula_ipi, data = pdata_adv, model = "within")
re_ipi_adv <- plm(formula_ipi, data = pdata_adv, model = "random",
                  random.method = "walhus")  # or "amemiya"
```

```{r ipi-adv-table, results='asis'}

stargazer(pols_ipi_adv, fe_ipi_adv, re_ipi_adv,
          title          = "IPI Regression — Advanced Exporters",
          column.labels  = c("Pooled OLS", "Fixed Effects", "Random Effects"),
          dep.var.labels = "ln(IPI)",
          covariate.labels = c("Oil Shock (% $\\Delta$ Brent)",
                               "ln(NEER)", "Policy Rate (%)",
                               "VIX", "Post-Crisis Dummy"),
          keep.stat      = c("n", "rsq", "adj.rsq"),
          type           = "latex", style = "aer",
          digits         = 6,
          digits.extra   = 4,
          notes          = "Arellano HC3 robust SE applied in Section 8.",
          notes.align    = "l")
```


---

# Diagnostic Tests and Robust Standard Errors

## Hausman Test (FE vs. RE)

```{r hausman}
# Emerging Importers
haus_cpi_emg <- phtest(fe_cpi_emg, re_cpi_emg)
haus_ipi_emg <- phtest(fe_ipi_emg, re_ipi_emg)

cat("=== Hausman Test — CPI (Emerging Importers) ===\n")
print(haus_cpi_emg)
cat(if (haus_cpi_emg$p.value < 0.05)
  "\n-> p < 0.05: Reject H0. Fixed Effects preferred.\n"
  else
  "\n-> p >= 0.05: Fail to reject H0. Random Effects acceptable.\n")

cat("\n=== Hausman Test — IPI (Emerging Importers) ===\n")
print(haus_ipi_emg)
cat(if (haus_ipi_emg$p.value < 0.05)
  "\n-> p < 0.05: Reject H0. Fixed Effects preferred.\n"
  else
  "\n-> p >= 0.05: Fail to reject H0. Random Effects acceptable.\n")

# Advanced Exporters
haus_cpi_adv <- phtest(fe_cpi_adv, re_cpi_adv)
haus_ipi_adv <- phtest(fe_ipi_adv, re_ipi_adv)

cat("\n=== Hausman Test — CPI (Advanced Exporters) ===\n")
print(haus_cpi_adv)
cat(if (haus_cpi_adv$p.value < 0.05)
  "\n-> p < 0.05: Reject H0. Fixed Effects preferred.\n"
  else
  "\n-> p >= 0.05: Fail to reject H0. Random Effects acceptable.\n")

cat("\n=== Hausman Test — IPI (Advanced Exporters) ===\n")
print(haus_ipi_adv)
cat(if (haus_ipi_adv$p.value < 0.05)
  "\n-> p < 0.05: Reject H0. Fixed Effects preferred.\n"
  else
  "\n-> p >= 0.05: Fail to reject H0. Random Effects acceptable.\n")
```

## Breusch-Pagan LM Test (RE vs. POLS)

```{r breusch-pagan}
bp_cpi_emg <- plmtest(pols_cpi_emg, effect = "individual", type = "bp")
bp_ipi_emg <- plmtest(pols_ipi_emg, effect = "individual", type = "bp")
bp_cpi_adv <- plmtest(pols_cpi_adv, effect = "individual", type = "bp")
bp_ipi_adv <- plmtest(pols_ipi_adv, effect = "individual", type = "bp")

cat("=== BP Test — CPI (Emerging Importers) ===\n"); print(bp_cpi_emg)
cat("\n=== BP Test — IPI (Emerging Importers) ===\n"); print(bp_ipi_emg)
cat("\n=== BP Test — CPI (Advanced Exporters) ===\n"); print(bp_cpi_adv)
cat("\n=== BP Test — IPI (Advanced Exporters) ===\n"); print(bp_ipi_adv)
```

## Robust Standard Errors

```{r robust-se}
cat("=== FE CPI — Emerging Importers | Arellano HC3 ===\n")
coeftest(fe_cpi_emg, vcov = vcovHC(fe_cpi_emg, method = "arellano", type = "HC3"))

cat("\n=== FE IPI — Emerging Importers | Arellano HC3 ===\n")
coeftest(fe_ipi_emg, vcov = vcovHC(fe_ipi_emg, method = "arellano", type = "HC3"))

cat("\n=== FE CPI — Advanced Exporters | Arellano HC3 ===\n")
coeftest(fe_cpi_adv, vcov = vcovHC(fe_cpi_adv, method = "arellano", type = "HC3"))

cat("\n=== FE IPI — Advanced Exporters | Arellano HC3 ===\n")
coeftest(fe_ipi_adv, vcov = vcovHC(fe_ipi_adv, method = "arellano", type = "HC3"))
```

## Coefficient Comparison Plot

```{r coef-plot, fig.cap="Oil Shock Coefficient on ln(CPI): Emerging Importers vs Advanced Exporters"}
extract_coef <- function(model, label) {
  ct  <- coeftest(model, vcov = vcovHC(model, method = "arellano", type = "HC3"))
  est <- ct["oil_pct_change", "Estimate"]
  se  <- ct["oil_pct_change", "Std. Error"]
  data.frame(Group    = label,
             Estimate = est,
             CI_low   = est - 1.96 * se,
             CI_high  = est + 1.96 * se)
}

coef_df <- rbind(
  extract_coef(fe_cpi_emg, "Emerging Importers\n(Main Group)"),
  extract_coef(fe_cpi_adv, "Advanced Exporters\n(Comparison Group)")
)

ggplot(coef_df, aes(x = Group, y = Estimate, color = Group)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),
                width = 0.15, linewidth = 0.9) +
  geom_point(size = 5) +
  scale_color_manual(
    values = c("Emerging Importers\n(Main Group)"      = "#e74c3c",
               "Advanced Exporters\n(Comparison Group)" = "#2980b9")) +
  labs(title    = "Oil Shock Coefficient on ln(CPI) by Country Group",
       subtitle = "Fixed Effects model; bars = 95% CI (Arellano HC3)",
       x = NULL, y = "Coefficient Estimate") +
  theme_minimal(base_size = 13) +
  theme(plot.title = element_text(face = "bold"),
        legend.position = "none")
```

---


